---
title: "Nuts and chicken"
author: "Lukas Gürtler & Frederik Kuhl"
output: html_document
bibliography: 
  - bib/references.bib 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(decisionSupport)
library(tidyverse)
library(knitr)
library(readxl)
library(rmarkdown)
```

```{r add_R_bib, include=FALSE}
knitr::write_bib(c(.packages(),
                   'knitr', 'decisionSupport'), 'bib/packages.bib')
```

This supplementary is available under <https://github.com/FreKuhl/Nuts_and_chicken.git> and outlines the Decision Analysis approaches used in Model-based evaluation of management options in ornamental plant nurseries [@ruett_model-based_2020]. Here we provide our input table, code and results to allow for transparent reproduction of the model.

All other applied `R` packages are cited and listed in the [References].

## Input table
The input table `Input_estimates.xlsx` (attached) contains: Variable names, unit, distributions (posnorm = positive normal distribution, const = constant, tnorm_0_1= truncated normal distribution, norm = normal distribution), lower bound, mean, upper bound and definition of variables.

## Implementing the model in R

Here we provide our mathematical model that enables simulation of decision outcomes.
The calculations in this document are based on random draws from the distributions in the input table `Input_estimates.csv`. Explanations for code chunks are not part of the actual simulation. 

Load the input table `Input_file.csv` and make variables.
```{r eval= FALSE}
input_estimates <- read_excel("input_estimates.xlsx")

make_variables <- function(est,n=1)
{ x <- random(rho=est, n=n)
for(i in colnames(x)) assign(i, as.numeric(x[1,i]),envir = .GlobalEnv)}

make_variables(as.estimate(input_estimates))
```

We generated a function called `model_function` to evaluate the decision options in `decisionSupport` [@luedelingDecisionSupportQuantitativeSupport2019]. The following calculations are part of this function (see the entire function below). 
```{r eval= FALSE}
model_function <- function() {}
```

# References